---
title: "p8105_hw5_yw3438"
author: "Yuning Wang"
date: "10/31/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)
library(purrr)
library(viridis)

set.seed(10)
```

## Problem 1

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>% 
  janitor::clean_names()
```



```{r}
replace_measure = function(x) {
  
  if (is.numeric(x)) {
    replace(x, is.na(x), mean(x, na.rm = TRUE))
  } else if (is.character(x)) {
    replace(x, is.na(x), "virginica")
  }
  
}


output = map(iris_with_missing, replace_measure)
output

```



## Problem 2

```{r message=FALSE, warning=FALSE}
# Read in and tidy the filenames into a dataframe
files_name = data.frame(list.files("./data")) 
colnames(files_name) = "file_name"

# Write a function to read in the data of all the files
read_data = function(x) {
  
  read_csv(paste0("./data/", x)) 
  
}

# Save the results in a column in the dataset
file_datas = files_name %>% 
  mutate(data = purrr::map(files_name$file_name, read_data)) %>% 
  unnest()

# Tidy the data
file_data_tidy = file_datas %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "data"
  ) %>% 
  mutate(file_name = str_remove(file_name, ".csv"),
         week = str_remove(week, "week_")) %>% 
  separate(file_name, c("group", "subject_id"), sep = "_") %>% 
  mutate(group = recode(group, "con" = "control", 
                        "exp" = "experimental"))

# Draw a lineplot that reflect
file_data_tidy %>% 
  ggplot(aes(x = week, y = data, 
             color = subject_id, group = subject_id)) + 
  geom_point(alpha = .5) + 
  geom_line() +
  theme_bw() +
  theme(legend.position = "bottom") +
  labs(
    x = "Week",
    y = "Data Value",
    title = "Observations on Each Subject Over Time"
  ) +
  viridis::scale_color_viridis(
    name = "Subject ID", 
    discrete = TRUE
  ) +
  facet_grid(~group)
```

From the plot above, it can be discovered that in the control group the data values fluctuated from week 1 to week 8 but the observations' data value almost remain the same.  
  
The plot of experimental group shows that the observation data values gradually and fluctuately increased from week 1 to week 8, which had difference from the control group.  
  
The two plots showed that the exposure of interest might have a promotion effect on the subjects.


## Problem 3

Write the function for simple linear regression
```{r}
sim_regression = function(n = 30, beta0 = 2, beta1) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, sqrt(50))
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  ls_tidy = broom::tidy(ls_fit) %>% 
    janitor::clean_names()
  
  tibble(
    beta1_hat = ls_tidy$estimate[[2]],
    p_value = ls_tidy$p_value[[2]]
  )
}
```

Set beta1 = 0. Generate 10000 datasets from the model. Save the results beta1_hat and p-value arising from the test of H: beta1 = 0.

```{r}
set.seed(10)
#save the results into sim_results
sim_results = 
  rerun(10000, sim_regression(30, 2, 0)) %>% 
  bind_rows() 

head(sim_results)
```

Repeat the process above for beta1 = 1, 2, 3, 4, 5, 6

```{r}
sim_results_6 = 
  tibble(beta1_value = c(1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output_lists = map(.x = beta1_value, 
                       ~rerun(10000, sim_regression(beta1 = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs)

head(sim_results_6)
```

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of beta1 on the x axis.

```{r}
#read in the data
sim_results_6 %>% 
  group_by(beta1_value) %>% 
  mutate(n_sum = n()) %>% 
  # find out all the proportion of beta1 should be rejected
  filter(p_value < 0.05) %>% 
  group_by(beta1_value) %>% 
  mutate(n_reject = n(),
         power = n_reject / n_sum) %>% 
  select(beta1_value, power) %>% 
  distinct() %>% 
  #draw the plot
  ggplot(aes(x = beta1_value, y = power, fill = beta1_value)) +
  geom_col() +
  theme_bw() +
  theme(legend.position = "bottom") +
  labs(
    x = "Beta1 Values",
    y = "Power",
    title = "Power in Simple Linear Regressions"
  ) +
  viridis::scale_color_viridis(
    name = "Beta1 value", 
    discrete = TRUE
  )
```







